### 2014-10-20 thesis/method/classification.tex
Wrote about 0R and 1R and created acronyms for the classifiers #12

Since we will be using supervised learning techniques, we need
\textit{training examples}, which consist of a set of feature vectors
that are already labelled with the class that it belongs in. These
training examples are then used by a classifier to ``learn'' the
relationship linking the feature vectors to their class labels. In this
chapter we describe each of the learning algorithms we used to model the
relationship between the feature vectors and the LOS.

\section{ZeroR and OneR}

\section{Na\"{i}ve Bayes}

\section{Decision Tree (C4.5)}

\section{Logistic Regression}

@@

\section{$k$-Nearest Neighbour}
\subsection{Basic Algorithm}

@@

\section{Feed-forward Neural Network}

>>>>

Since we will be using supervised learning techniques, we need
\textit{training examples}, which consist of a set of feature vectors
that are already labelled with the class that it belongs in. These
training examples are then used by a classifier to ``learn'' the
relationship linking the feature vectors to their class labels. Once we have
``trained'' the classifier to learn this relationship with the pre-labelled
data, it will then be able to predict the class of any feature vector that we
give it.

In this
chapter we describe each of the learning algorithms we used to model the
relationship between the feature vectors and the LOS.

\section{0R and 1R}
Short for ``0-rule'' and ``1-rule'' respectively, 0R and 1R are
very simple classifiers. 0R uses no features to predict the class, and
1R only uses one.

Given a data set, the 0R classification algorithm will find the class that
occurs the most often, and predict this class for all new examples. For LOS
classification, if one class in a data set was ``LOS $\leq$ 2 days'' and
the other was
``LOS $>$ 2 days'', and feature vectors (which represent patients in this
scenario) were more commonly labelled ``LOS $\leq$ 2 days'', then 0R will
predict all unseen patients with ``LOS $\leq$ 2 days''.
The prediction decision of 0R is very easy to understand,
and its results also provide an apt baseline for evaluating the more
sophisticated classifiers used in this work.

1R works by considering each feature individually.
For each of the values of the
feature, 1R finds the class with the highest frequency and creates a rule
from this observation. If the feature is numeric (that is, its values are
continuous rather than discrete), then 1R will partition the spectrum of
values into discrete buckets. \todo{describe buckets more}
The error rate, expressed as the ratio of correct predictions to the total
number of examples in the data set,
is calculated for each rule that is generated
in this way. The rule with the lowest error rate is then chosen as the 1-rule
for this classifier,
and if there is a tie, it is broken randomly. As with 0R, the prediction
decision of 1R is transparent and it provides another baseline upon which
more sophisticated classifiers can be evaluated.

Concretely, given a feature
vector of the form \textit{(age, gender, has\_cancer)},
1R will split the ages of
all patients into discrete categories
(such as \textit{0-20, 21-40, 41-65, 66+}). It
will then check the class labels for all training examples in the data set
that have \textit{age} in the 0-20 category
(as that is the first value for the partitioned \textit{age} feature) and
note the most common class, proceeding similarly for the rest of the
categories of \textit{age}. Then it will consider \textit{gender}, which has
two possible values $\{$\textit{male, female}$\}$, and finally \textit{has\_cancer}
with two values $\{$\textit{true, false}$\}$. This results in 8 rules,
corresponding to three features.
An example of a rule is that \textit{age 0-20} most commonly
has ``LOS $\leq$ 2 days''. For each of these rules, 1R will attempt to
use only that rule to predict the LOS class for each example in the data set,
noting down the error rate. 1R then chooses the feature that produces rules
with the lowest total error rate. \todo{maybe add a table}

\section{Na\"{i}ve Bayes (NB)}
Unlike 1R, which considers only one feature in the

\section{C4.5 Decision Tree (DT)}

\section{Logistic Regression (LR)}

@@

\section{$k$-Nearest Neighbour (kNN)}
\subsection{Basic Algorithm}

@@

\section{Feed-Forward Neural Network}
